Fastest Paths Between Points in $\R^2$ for a Particle Moving with Constant Speed and Bounded Centripetal Acceleration

### 2013-10-11 fixed_speed_theorems.tex
Edits

At the beginning of our paper we mentioned that there is a case when a particle is too close to the ending position and can't turn fast enought, so it ends up passing by it. We formalize this notion in the following lemma.

\begin{lemma}\label{lem:too-close}
  Let particle $p$ have constant speed, bounded centripetal acceleration, an initial angle $\theta_0$, starting position $\bvec{X_0}$, and ending position $\bvec{X_f}$. Every valid path where $\theta(t)$ is minimized for all $t \in [T_0(\bhat{\gamma_p}), T_f(\bhat{\gamma_p})]$ has $d(\bvec{X_0}, \bvec{X_f}) \ge 2 R_{min} \cos\paren{\theta_0}$.
\end{lemma}

  The following figure will help illustrate the theorem.

  \begin{figure}[H]
    \begin{center}
      \includegraphics[width=3.5in,height=2.5in,keepaspectratio]{valid_trajs.eps}
    \end{center}
  \vspace{-.2in} % corrects bad spacing
  \caption{\label{fig:valid-traj}}
  \end{figure}

  One should notice that if $X_f$ is any position inside the circle of radius $R_{min}$, such as point B, then the path is invalid. It is not possible to turn inside the circle, because the centripetal acceleration is bounded. Thus, C is the closest valid ending position. C is a distance $2 R_{min} \cos\paren{\theta_0}$ away from A.

\end{proof}

@@

Now let us introduce a particle $p_2$ with the same conditions as $p_1$, but different centripetal acceleration. For some small enough $\epsilon > 0$, we can now find a time interval $t \in [t_b-\epsilon, t_b+\epsilon]$ where that $a_{c,2}(t) < a_{c,1}$.  We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after $t_b$ is strictly worse than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.

@@

Looking at Equation \ref{eq:theta-diff}

>>>>

@@

Now let us introduce a particle $p_2$ with the same conditions as $p_1$, but different centripetal acceleration at some time $t_b$. Suppose for some small $\epsilon > 0$, we have a time interval $t \in [t_b-\epsilon, t_b+\epsilon]$ where that $a_{c,2}(t) < a_{c,1}$.  We shall show that the fastest path for $p_2$, $\hat{\gamma_2(t)}$, after $t_b$ is strictly worse than the fastest path for $p_1$, $\hat{\gamma}_1$, which will allow us to conclude that $\gamma_1(t)$ is the unique fastest path.

@@

Looking at Equation \ref{eq:theta-diff} and recalling that $a_{c,2}(t_b) - a_{c,1}(t_b) < 0$.

### 2013-10-11 introduction.tex
Edits

The problem of finding fastest paths between two points (let's call them A and B) is interesting because many attributes of a fastest path are intuitively obvious, but rigorously proving them is much more difficult. One's first assumption would be that the fastest path between A and B, would be to travel in a straight line from A to B. This would be true in the simple case where the turning rate is not constrained, but it is not true in the general case when a particle has a constrained turning rate and starts with some nonzero velocity not directed towards B. In the general case, it is easier to turn towards B, the further one is away from it, so there is the possibility that it would be fastest for the particle to turn away from B for a short period of time, so that it can then turn towards it more quickly. In fact, if the particle is too close to B, it won't have time to turn towards it, and will pass by B.

@@

Given a particle in $\R^2$ starts at a position A in with an initial velocity, what is the path in for the particle to take to reach a final position B, such that the time spent traveling from A to B is minimized. The particle can have restrictions on its position, velocity, and acceleration. Our model problem has fixed speed and a bounded turning rate.

>>>>

The problem of finding fastest paths between two points (let's call them A and B) is interesting because many attributes of a fastest path are intuitively obvious, but rigorously proving them is much more difficult. One's first assumption would be that the fastest path between A and B would be to travel in a straight line from A to B. This would be true in the simple case where the turning rate is not constrained, but it is not true in the general case when a particle has a constrained turning rate and starts with some nonzero velocity which is not directed towards B. In the general case, it is easier to turn towards B the further one is away from it.

@@

Our problem is the following: given a particle in $\R^2$ starting at position A with some initial velocity, what is the path that the particle must take to reach a final position B such that the time spent traveling from A to B is minimized? The particle can have restrictions on its position, velocity, and acceleration. Our model problem has fixed speed and a bounded turning rate.

### 2013-10-11 path_theorems.tex
Added paper.pdf.
Fix final thm.
Edits

\begin{theorem}\label{thm:theta-min}
  Let $p$ be a particle with bounded tangential acceleration and initial position $X_0$. A path $\gamma_1$ to $\bvec{X_f}$ is a fastest path if, for every other valid path $\gamma_2$ to $\bvec{X_f}$, $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$. The fastest path is unique if all the inequalities are strict.

@@

  \[r(t) = r(T_0) + \int_{t' = T_0}^{t} - v(t) \cos(\abs{\theta(t)})\]

  Thus, if $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$, then $r_1(t) \le r_2(t)$, and $T_f(\gamma_1) \le T_f(\gamma_2)$, so $\gamma_1$ is a fastest path. If all the inequalities are strict, then $T_f(\gamma_1) < T_f(\gamma_2)$, so every other path is longer, and thus $\gamma_1$ is the unique fastest path.

@@

  \begin{align*}
    v_2(t)& = \int_{t'=T_0(\gamma_2(t))}^{t} a_{t, 2} dt\\
    & \le \bar{a_t} t\\
    &  \le v_1(t)
  \end{align*}

>>>>

\begin{theorem}\label{thm:theta-min}
  Let $p$ be a particle with bounded tangential acceleration and initial position $X_0$. A path $\gamma_1$ to $\bvec{X_f}$ is a fastest path if, for every other valid path $\gamma_2$ to $\bvec{X_f}$, $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$. The fastest path is unique if one of the inequalities is strict.

@@

  \[r(t) = r(T_0) + \int_{t' = T_0}^{t} - v(t') \cos(\abs{\theta(t')}) dt'\]

  Thus, if $\abs{\theta_1(t)} \le \abs{\theta_2(t)}$ and $v_1(t) \le v_2(t)$, then $r_1(t) \le r_2(t)$. Because the distance that needs to be traveled by $p_2$ is greater at time any $t$, and because $v_1(t) \le v_2(t)$, then we know that $T_f(\gamma_1) \le T_f(\gamma_2)$. Therefore $\gamma_1$ is a fastest path. If all the inequalities are strict, then $T_f(\gamma_1) < T_f(\gamma_2)$, so every other path is longer, and thus $\gamma_1$ is the unique fastest path.

@@

  \begin{align*}
    v_2(t)& = \int_{t'=T_0(\gamma_2}^{t} a_{t, 2}(t') dt'\\
    & \le \bar{a_t} t\\
    &  \le v_1(t)
  \end{align*}
